A New Method of Modelling Tuneable Lasers with Functional Composition

### 2019-11-15 Papers/Journal/Tuneable_Lasers.tex
Fixed figure

\begin{figure}
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.7in lw 3}]
load '/home/brady/Templates/YGB.p'
#set format x '%.1f'
#set format y '%.1f'
set format z '%.1f'
set grid
set yl '$T$'
set zl '$|A|$'
set ztics 0.5

set yr [-2.5:2.5]

set xtics ('Loss' 3, 'Disp.' 9, 'Mod.' 15, 'Gain' 21)

set xtics center offset 0,-0.5

set xyplane 0

set view 45,325,1.25

unset colorbox

sp 'EBig.dat' u ($2*0.1):1:3 w pm3d not, \
'Shell1.dat' u 2:1:3 w l lw 0.2 lc 8 not, \
'Shell2.dat' u ($2*0.1):1:3 w l lw 0.2 lc 8 not
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\includegraphics{Evo}
\caption{}
\label{fig:}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{Conv}
\caption{}
\label{fig:}
\end{figure}
